Preregistration

### 2019-05-13 analysis/survey/preregistration.Rmd
Flesh out hypotheses

We use a conjoint survey experiment to examine the impact of organizational and structural features of nongovernmental organizations (NGOs) on their donors’ decisions to engage in philanthropy. We explore three research questions in this study:

@@

For our first set of questions, we predict that: (TODO: finish these)

- Donors will be more likely to donate to NGOs facing government criticism and crackdown
- Donors will be more likely to donate to less contentious NGOs (i.e. those focused on emergency response and refugee relief)
- Donors will be more likely to donate to NGOs that are privately funded and that many small private donations will have a larger effect than a handful of wealthy donors.
- Donors will be more likely to donate to NGOs that engage in financial transparency
- Donors will be more likely to donate to NGOs that engage in accountability

@@

- Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs trust + Public affairs activity`
- Ideology: `Dnation preferences ~ Political ideology + Social ideology + Religiosity`
- Charity and voluntarism: `Donation preferences ~ Charity trust + Charity activity + Volunteer activity + Activism activity + Association membership`
- Demographics: `Donation preferences ~ Gender + Marital status + Education + Income + Race + Age`

@@

- `Donation preferences ~ Public affairs + Ideology`
- `Donation preferences ~ Public affairs + Ideology + Charity and voluntarism`
- `Donation preferences ~ Public affairs + Ideology + Charity and voluntarism + Demographics`

>>>>

We use a conjoint survey experiment to examine the impact of organizational features of nongovernmental organizations (NGOs) and the structural factors in target countries in which they operate on donors’ decisions to engage in philanthropy. We explore three research questions in this study:

@@

For our first set of questions, we predict that:

1. **Branding**

    - Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace [Mechanism: awareness of need and contentiousness of issue area]

2. **Government crackdown**

    - Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism [Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively. This perception of efficacy leads to increased donations.]
    - Donors will show increased willingness to donate to Oxfam and Red Cross when they are facing government crackdown or criticism compared to when Amnesty or Greenpeace is facing crackdown.

3. **Issue area**

    - Donors will show increased willingness to donate to NGOs working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights) 
    - Donors will show increased willingness to donate to NGOs facing government crackdown/criticism working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights) [Mechanisms: Perceptions of deservingness of NGOs dealing with emergency response and refugee relief. Donors are also more likely to donate to programs that are compatible with government preferences and have easily measurable outputs, which environment and human rights programs often lack. NGOs working on more contentious issue areas may be expelled or shut down, which would be a waste of donor resources, make it less likely that they donate to these groups.]

4. **Funding sources**

    - Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealhty private donors and government grants [Mechanism: Perception of efficacy - your contribution matters as a small donor. Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.]
    - Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors
    - Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors and work in less contentious areas (emergency response and refugee relief)

5. **Organizational practices**

    - Donors will show increased willingness to donate to NGOs that are financially transparent [Mechanism: Perception of efficacy]
    - Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent
    - Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and are funded primarily by numerous small private donors
    - Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) 
    - Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors
    - Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits [Mechanism: Donors don't necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks]

@@

- Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs activity`
- Political ideology: `Donation preferences ~ Political ideology`
- Social views: `Donation preferences ~ Public affairs trust + Social ideology + Religiosity`
- Charity and voluntarism: `Donation preferences ~ Charity trust + Charity activity + Volunteer activity + Activism activity + Association membership`
- Demographics: `Donation preferences ~ Gender + Marital status + Education + Income + Race + Age`

@@

- `Donation preferences ~ (Public affairs) + (Political ideology)`
- `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views)`
- `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism)`
- `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism) + (Demographics)`
